---
title: "**Short title:** Flexdashboard poster template"
output: 
  postr::flex_dashboard_poster:
    render_print: TRUE
classoption: landscape
    #css: ["resources/fontawesome-all.css"]
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(hrbrthemes)
library(patchwork)
library(ggpubr)

#hrbrthemes::import_roboto_condensed()

#library(webshot)
#webshot("file:///Users/linhnguyen/Desktop/BIS498/SMALS2/my_poster.html", "my_poster.png", expand = c(40, 20, 40, 20))

#nitr::opts_chunk$set(echo = TRUE)
#devtools::install_github("odeleongt/postr")
#webshot::install_phantomjs()
#postr::render("my_poster/my_poster.Rmd")
load('SMALS.Rdata')
```

## Header row {data-height=15}

###

<table style="width:100%, padding: 30px 30px 10px;">

<tr style="background-color:#4B2E83;">
  <td><h1 style = "color:white;margin-left:50px;">
  **Student-made Models Analyzed at Large Scales (SMALS)**
  </h1>
  
  <img src = "figure/yellow_line.png" align = "left" style = "width:5%; height:10%;"></img>
  <img src = "figure/yellow_line.png" align = "left" style = "width:5%; height:10%;"></img>
  <img src = "figure/yellow_line.png" align = "left" style = "width:5%; height:10%;"></img>

  <br></br>
  <h4 style = "color:white;margin-left:50px;"> **Linh Nguyen, Scott Corbitt, Emmanuel Gabriel, Darcie Nelson, Prim Bunyakiat, Caleb Trujillo** </h4> 
  <h4 style = "color:white;margin-left:50px;"> University of Washington Bothell</h4>
  </center></td>
  <td rowspan="2">
  <img src = "https://www.washington.edu/wp-content/themes/be-boundless/campaign/img/W-Logo_White.png" align = "right" style= "width:80%;">
  </img>
  </td>
  
</tr>

</table> 
<hr>

**Abstract** 




## Body row {data-height=75}

<table style= "padding-bottom:30px;padding-left: 30px;padding-right: 30px;"></table>


### **Intro** {data-width=300}

#### Research Question 
How cognitive network growth as  explanation of the learning processes evident in student models?

#### Objective
1. Explore the use of network approaches as a means to assess learning evident in models made by students in biology and statistics.

Explore the use of network approaches as a means to assess learning evident in models made by students by statistics

#### Project impact
The project will further an understanding of models used in STEM education and strengthen interdisciplinary connections between disparate fields such as data science, learning theory, and discipline-specific education. In doing this, our research can provide evidence that fulfills recommendations from leaders on policy regarding educational changes

### **Column 2 title** {data-width=700}

```{r}
ggarrange(figcohesion + theme(aspect.ratio=1),figdiameter  + theme(aspect.ratio=1),figcentrality  + theme(aspect.ratio=1), nrow = 1, common.legend = TRUE, legend = "none")
```

## Footer row {data-height=1} 

### {data-width=50}


### {data-width=50 .small}


In collaboration with Tammy Long at Michigan State University

